Results from the deep learning challenge associated with the 3MD4040 lecture on plankton classification

### 2022-07-10 Report/paper.tex
remove the neurips notice string
fix fig position
more on teams report

		\begin{table}
			\begin{tabular}{p{3cm}|p{3cm}|p{3cm}|p{3cm}|p{3cm}|p{3cm}|p{3cm}}
			Participant & Data preprocessing & Train augmentation & Test augmentation & Model architectures & Optimizer and scheduler & Class imbalance \\
			\hline
			Metz Dream Deep & 
			Resize($224$), Normalize($0.5$, $0.5$) & 
				Rotate($0, 360$), HFlip($0.5$), Translate($0.2$), Normalization$(0.5, 0.5$)&
			None&
			&
				Cross entropy loss, Adam($1e-4$), Weight decay $1e-4$, ..., batch size $128$, train/valid split&
			batch sampler $f_k=1/count_k$\\
			\hline
			The Backpropagated StuBBorns & 
			Resize($224$), Normalize($0.5$, $0.5$) & 
			&
			&
			&
			&
			\\
			\hline
			JMBmc & 
			Resize($224$), Normalize($0.5$, $0.5$) & 
			&
			&
			&
			&
			\\
			\hline
			AG0D & 
			Resize($224$), Normalize($0.5$, $0.5$) & 
			&
			&
			&
			&
			\\
			\hline
		\end{tabular}
			\caption{Overview of the experiments of the participants. Part 2. \label{table:overview2}}
	\end{table}

		\begin{table}
			\begin{tabular}{p{3cm}|p{3cm}|p{3cm}|p{3cm}|p{3cm}|p{3cm}|p{3cm}}
			Participant & Data preprocessing & Train augmentation & Test augmentation & Model architectures & Optimizer and scheduler & Class imbalance \\
			\hline
			ResMetz & 
			Resize($224$), Normalize($0.5$, $0.5$) & 
			&
			&
			&
			&
			\\
			\hline
			CelestineFeuillat & 
			Resize($224$), Normalize($0.5$, $0.5$) & 
			&
			&
			&
			&
			\\
			\hline
			LesJongleurs & 
			Resize($224$), Normalize($0.5$, $0.5$) & 
			&
			&
			&
			&
			\\
			\hline
			DeepBeru4s & 
			Resize($224$), Normalize($0.5$, $0.5$) & 
			&
			&
			&
			&
			\\
			\hline
			The Whale Sharks & 
			Resize($224$), Normalize($0.5$, $0.5$) & 
			&
			&
			&
			&
			\\
		\end{tabular}
			\caption{Overview of the experiments of the participants. Part 3. \label{table:overview3}}
	\end{table}
	\end{landscape}
	\clearpage
}

@@

\begin{figure}
	\begin{center}
		\raisebox{-0.5\height}{\includegraphics[width=0.25\columnwidth]{figs/class_f1_scores_per_team.pdf}}
		\hspace*{.4in}
		\raisebox{-0.5\height}{\includegraphics[width=0.62\columnwidth]{figs/class_f1_scores_per_class.pdf}}
	\end{center}
	\caption{\label{fig:class_f1_scores} Class F1 scores on the test data per team (left) and per class (right).}
\end{figure}

>>>>

		\begin{table}
			\begin{tabular}{p{3cm}|p{3cm}|p{3cm}|p{3cm}|p{3cm}|p{3cm}|p{3cm}}
			Participant & Data preprocessing & Train augmentation & Test augmentation & Model architectures & Optimizer and scheduler & Class imbalance \\
			\hline
			Metz Dream Deep & 
			Resize($224$), Normalize($0.5$, $0.5$) & 
				Rotate($0, 360$), HFlip($0.5$), Translate($0.2$), Normalization$(0.5, 0.5$)&
			None& Custom CNNs, resnet34, VGG16, VGG19, regnet\_y\_32gf
			&
				Cross entropy loss, Adam($1e-4$), Weight decay $1e-4$, ..., batch size $128$, train/valid split (0.95, 0.05)&
			batch sampler $f_k=1/count_k$\\
			\hline
			The Backpropagated StuBBorns & 
				SquarePad(), Resize($224$), Normalize($0.485$, $0.229$) & torchvision AutoAugment &None
			& pretrained timm efficientnetv2\_rw\_s, tf\_efficientnet\_b8\_ap, deit\_tiny, cait\_s24\_224, coat\_mini, swin transformers, tnt\_s\_patch16\_224, dm\_nfnet, resnet50 followed by 2 linear/dropout/relu layers
				& Cross Entropy Loss, Adam($1e-4$), early stopping on the validation loss, batch size $32$, train/valid split ($0.8, 0.2$) 
			&
			batch sampler $f_k=1/count_k$\\
			\hline
			JMBmc & 
				Resize($224$), 3 chans ImageNet Normalize & RandomRotate($30$), HFlip($0.5$), VFlip($0.5$)
			& None
				& pretrained timm tf\_efficient\_b4, pretrained torchvision, possibly frozen, feature extraction with resnet50, wideResnet50, mobilenet\_v2 followed by $5$ linear/dropout layers\footnote{unfortunately, in their implementation, the participants forgot to add non linearities between the layers, the classification stage is therefore only linear although composed of a stack of layers}
				& Cross entropy loss, SGD($0.03$) with momentum, StepLR scheduler, batch size $64$, train/valid split ($0.8, 0.2$), early stopping on the validation loss
			&None
			\\
			\hline
			AG0D & 
				Resize($224$), 3 chans Imagenet Normalize & RandomRotate, RandomAffine, HFlip($0.5)$, VFlip($0.5$), 
			& RandomRotate, RandomAffine, HFlip($0.5)$, VFlip($0.5$), 
				& Custom CNNs, pretrained torchvision Resnet18, Resnet50, EfficientNetB7 ... with a random classification head\footnote{unfortunately, as JMBmc, the classifier is a stack of linear layers without non linearities}
				& weighted cross entropy loss, Adam($0.001$), Reduce LR on plateau, batch size $64$, early stopping on the validation F1, train/valid split ($0.88, 0.12$), per class
				& class weights in the CE loss $w_k=\log(\sum_i count_i/count_k) > 0$
			\\
			\hline
		\end{tabular}
			\caption{Overview of the experiments of the participants. Part 2. \label{table:overview2}}
	\end{table}

		\begin{table}
			\begin{tabular}{p{3cm}|p{3cm}|p{3cm}|p{3cm}|p{3cm}|p{3cm}|p{3cm}}
			Participant & Data preprocessing & Train augmentation & Test augmentation & Model architectures & Optimizer and scheduler & Class imbalance \\
			\hline
			ResMetz & 
			SquarePad, Resize($224$), 3 chans ImageNet Normalize & 
				HFlip($0.3$), VFlip($0.3$), RandomRotate
			& None
			& torchvision pretrained Resnet18, Resnet50, EfficientNet with a random classification head
				& weighted cross entropy loss, Adam($3e-4$), early stopping the validation F1, train/valid split ($0.8, 0.2$)
			&
			class weights in the CE loss $w_k=\sqrt(\sum_i count_i/count_k)$, batch sampler with the same weight as the class weights

			\\
			\hline
			CelestineFeuillat & 
			Resize($224$), Normalize($0.5$, $0.5$) & 
			&
			&
			&
			&
			\\
			\hline
			LesJongleurs & 
			Resize($224$), Normalize($0.5$, $0.5$) & 
			&
			&
			&
			&
			\\
			\hline
			DeepBeru4s & 
			Resize($224$), Normalize($0.5$, $0.5$) & 
			&
			&
			&
			&
			\\
			\hline
			The Whale Sharks & 
			Resize($224$), Normalize($0.5$, $0.5$) & 
			&
			&
			&
			&
			\\
		\end{tabular}
			\caption{Overview of the experiments of the participants. Part 3. \label{table:overview3}}
	\end{table}
	\end{landscape}
	\clearpage
}

@@

\begin{figure}[htbp]
	\begin{center}
		\raisebox{-0.5\height}{\includegraphics[width=0.25\columnwidth]{figs/class_f1_scores_per_team.pdf}}
		\hspace*{.4in}
		\raisebox{-0.5\height}{\includegraphics[width=0.62\columnwidth]{figs/class_f1_scores_per_class.pdf}}
	\end{center}
	\caption{\label{fig:class_f1_scores} Class F1 scores on the test data per team (left) and per class (right).}
\end{figure}
